Deep Learning

### 2015-01-13 deepreview.tex
figured a few of the missing references

This architecture exploits the property that many natural signals are
{\em compositional hierarchies}. In images, local combinations of
edges form motifs, motifs assemble into parts, and parts form objects.
Similar hierarchies exists in speech and text from sounds to phones,
phonemes, syllables, words, and sentences. The elements that form
elements in the next level can vary in relative position and
appearance. The convolutional and pooling layers in ConvNets are
directly inspired by the classic notions of simple cells and complex
cells in visual neuroscience~\cite{Hubel1962}, and the overall
architecture is reminiscent of visual cortex ventral pathway hierarchy
LGN-V1-V2-V4-IT~\cite{VanEssen}. ConvNets have their roots in
Fukushima's Neocognitron~\cite{fukushima-82} whose architecture was
somewhat similar but did not have an end-to-end supervised learning
algorithm such as backpropagation+SGD.

@@

Since the early 2000s, there have been many tasks in which ConvNets
have been applied with success to the detection, segmentation, and
recognition of objects and regions in images. These were invariably
tasks in which labeled data was relatively abundant, such as traffic
sign recognition~\cite{sermanet-ijcnn-11,schmidhuber-traffic}, the
segmentation of biological images~\cite{ning-05} particularly for
connectomics~\cite{seung-xx}, the detection of faces, text, and human bodies in natural
images~\cite{vaillant-monrocq-lecun-94,nowlan-platt-95,garcia-delakis-04,osadchy-07,nasse-09,taylor-xx,sermanet-cvpr-13,thompson-14}.

@@

Other applications of ConvNets that are gaining importance concern
natural language understanding~\cite{collobert-weston-xx}, and speech
recognition~\cite{sainath-xx}.

>>>>

This architecture exploits the property that many natural signals are
{\em compositional hierarchies}. In images, local combinations of
edges form motifs, motifs assemble into parts, and parts form objects.
Similar hierarchies exists in speech and text from sounds to phones,
phonemes, syllables, words, and sentences. The elements that form
elements in the next level can vary in relative position and
appearance. The convolutional and pooling layers in ConvNets are
directly inspired by the classic notions of simple cells and complex
cells in visual neuroscience~\cite{Hubel62}, and the overall
architecture is reminiscent of visual cortex ventral pathway hierarchy
LGN-V1-V2-V4-IT~\cite{VanEssen}. ConvNets have their roots in
Fukushima's Neocognitron~\cite{fukushima-82} whose architecture was
somewhat similar but did not have an end-to-end supervised learning
algorithm such as backpropagation+SGD.

@@

Since the early 2000s, there have been many tasks in which ConvNets
have been applied with success to the detection, segmentation, and
recognition of objects and regions in images. These were invariably
tasks in which labeled data was relatively abundant, such as traffic
sign recognition~\cite{sermanet-ijcnn-11,Ciresan-et-al-2012}, the
segmentation of biological images~\cite{ning-05} particularly for
connectomics~\cite{Turaga2010}, the detection of faces, text, and human bodies in natural
images~\cite{vaillant-monrocq-lecun-94,nowlan-platt-95,garcia-delakis-04,osadchy-07,nasse-09,taylor-xx,sermanet-cvpr-13,Tompson-et-al-arxiv2014}.

@@

Other applications of ConvNets that are gaining importance concern
natural language understanding~\citep{collobert:2011b}, and speech
recognition~\cite{sainath-xx}.
